---
title: "exercise_reproducible"
author: "Leonie Thomas"
date: "2/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(openintro)
library(broom)
```


```{r}
tcga <- read.delim("/home/lthomas/Documents/Studium/Master/Seminare/Bioinfo_Seminare/R_course/Rcourse/inst/extdata/luad_tcga_pan_can_atlas_2018_clinical_data.tsv") 
tcga <- tcga[,apply(tcga,2,function(x){ !(sum(is.na(x)) == length(x))})] %>% 
            mutate(days_since_birth = Birth.from.Initial.Pathologic.Diagnosis.Date/356.25)

table(select(tcga,Diagnosis.Age))
table(select(tcga, Sex))
table(select(tcga, Race.Category))
table(tcga$American.Joint.Committee.on.Cancer.Tumor.Stage.Code)
```



## Chi-squared test

To look at the association between two categorical variables we can perform a chi squared test Study the relationshipo between sex and satisfaction.cat using a  contingency table and a bar plot.


```{r}

tcga %>% filter(!is.na(Sex))  %>% filter(!is.na(American.Joint.Committee.on.Cancer.Tumor.Stage.Code)) %>% ggplot(aes(Sex,fill=American.Joint.Committee.on.Cancer.Tumor.Stage.Code)) + geom_bar()

t <- tcga %>% select(Sex,American.Joint.Committee.on.Cancer.Tumor.Stage.Code) %>% table()
t
```


Use `prop.table` and  `geom_bar(stat="identity")` to report the relative frequencies of satisfaction between the sexes.

```{r}
prop.table(t, margin =1)

prop.table(t, margin =1) %>% as.data.frame() %>% ggplot(aes(x=Sex,y=Freq,fill=American.Joint.Committee.on.Cancer.Tumor.Stage.Code)) + geom_bar(stat="identity")

```


Test this relationship using the `chi.test` command on the contingency table.

```{r}
c<-chisq.test(t)
c
```




### Linear Regression

```{r}

tcga$Sex <- as.factor(tcga$Sex)
tcga$American.Joint.Committee.on.Cancer.Tumor.Stage.Code <- as.factor(tcga$American.Joint.Committee.on.Cancer.Tumor.Stage.Code) 

m1 <- lm(American.Joint.Committee.on.Cancer.Tumor.Stage.Code ~ Sex , data = tcga %>% filter(!is.na(Sex))  %>% filter(!is.na(American.Joint.Committee.on.Cancer.Tumor.Stage.Code)))
m1
tidy(m1)
```













